Ab Initio Effective One-Electron Potential Operators. II. Applications for Exchange-Repulsion Energy in Effective Fragment Potentials

### 2019-12-11 papers/3_oep_technique.Pauli/paper-r0.tex
Timing table added

\author{Wojciech Bartkowiak}

@@

{
\renewcommand{\arraystretch}{1.4}
\begin{table}[h]
\caption[]
{{\bf CPU timings in miliseconds of exchange\hyp{}repulsion single point 
energy calculations via various methods\footnotemark[1]}
}
\label{t:5}
\begin{ruledtabular}
\begin{tabular}{llccccccccc}
                      && \multicolumn{2}{c}{(H$_2$O)$_2$\footnotemark[2]} 
                      && \multicolumn{2}{c}{H$_2$O--HOCH$_3$\footnotemark[2]} 
                      && \multicolumn{2}{c}{(DMSO)$_2$\footnotemark[3]} \\
\cline{3-4}
\cline{6-7}
\cline{9-10}
Murrell et al.\footnotemark[4] && 3$\times 10^4$  & (10.0)  
                               && 3$\times 10^4$  & (10.0)
                               && 3$\times 10^4$  & (10.0) \\
Hayes-Stone\footnotemark[5]    && 3$\times 10^4$  & (10.0)  
                               && 3$\times 10^4$  & (10.0)
                               && 3$\times 10^4$  & (10.0) \\
EFP2                           && 3$\times 10^4$  & (10.0)  
                               && 3$\times 10^4$  & (10.0)
                               && 3$\times 10^4$  & (10.0) \\
OEP/large\footnotemark[6]      && 3$\times 10^4$  & (10.0)  
                               && 3$\times 10^4$  & (10.0)
                               && 3$\times 10^4$  & (10.0) \\
OEP/mini\footnotemark[6]       && 3$\times 10^4$  & (10.0)  
                               && 3$\times 10^4$  & (10.0)
                               && 3$\times 10^4$  & (10.0) \\
\end{tabular}
\end{ruledtabular}
%
\footnotetext[1]{1.2 GHz AMD EPYC\texttrademark{} 7301 16-Core Processor, calculations performed on 1 core. 
Exchange\hyp{}repulsion energies are given in parentheses for reference (kcal/mol).
See also the implementation details in the main text.}
\footnotetext[2]{Primary basis set: 6-311++G(d,p).}
\footnotetext[3]{Primary basis set: 6-31++G(d,p).}
\footnotetext[4]{Reference~\cite{Murrell.Randic.Williams.Longuet-Higgins.ProcRSocLondA.1965}.}
\footnotetext[5]{Reference~\cite{Hayes.Stone.MolPhys.1984}.}
\footnotetext[6]{Eq.~\eqref{}. Auxiliary basis sets for the EDF in $E^{\rm Rep}(S^{-1})$ 
from Eq.~\eqref{e:rep.murrell-etal.S1.oep}
are: `large' - aug-cc-pVDZ-jkfit for (H$_2$O)$_2$ and H$_2$O--HOCH$_3$ systems as well as
aug-cc-pVDZ-ri for (DMSO)$_2$ system;
`mini' - optimized small basis sets (see Supporting Information).}
%
\end{table}
}
%

>>>>

\author{Robert W. G{\'o}ra}
\author{Wojciech Bartkowiak}

@@

{
\renewcommand{\arraystretch}{1.4}
\begin{table*}[h]
\caption[]
{{\bf CPU timings in miliseconds of exchange\hyp{}repulsion single point 
energy calculations via various methods\footnotemark[1]}
}
\label{t:5}
\begin{ruledtabular}
\begin{tabular}{llccccccccc}
                      && \multicolumn{2}{c}{(H$_2$O)$_2$\footnotemark[2]} 
                      && \multicolumn{2}{c}{H$_2$O--HOCH$_3$\footnotemark[2]} 
                      && \multicolumn{2}{c}{(DMSO)$_2$\footnotemark[3]} \\
\cline{3-4}
\cline{6-7}
\cline{9-10}
Hayes \& Stone\footnotemark[4] && 1.16$\times 10^3$  & (4.81)  
                               && 1.12$\times 10^4$  & (4.72)
                               && 1.31$\times 10^5$  & (7.34) \\
Murrell et al.\footnotemark[5] && 2.33$\times 10^2$  & (4.53)  
                               && 3.87$\times 10^3$  & (4.44)
                               && 2.79$\times 10^4$  & (6.84) \\
EFP2                           && 0.496              & (4.45)  
                               && 0.84               & (4.44)
                               && 4.65   & (6.56) \\
OEP/large\footnotemark[6]      && 0.884  & (4.83)  
                               && 1.836  & (4.83)
                               && 8.95   & (6.77) \\
OEP/mini\footnotemark[6]       && 0.324  & (5.13)  
                               && 0.566  & (4.81)
                               && 3.00   & (7.41) \\
\end{tabular}
\end{ruledtabular}
%
\footnotetext[1]{1.2 GHz AMD EPYC\texttrademark{} 7301 16-Core Processor, calculations performed on 1 core. 
Exchange\hyp{}repulsion energies are given in parentheses for reference (kcal/mol).
See also the implementation details in the main text.}
\footnotetext[2]{Primary basis set: 6-311++G(d,p).}
\footnotetext[3]{Primary basis set: 6-31++G(d,p).}
\footnotetext[4]{Reference~\cite{Hayes.Stone.MolPhys.1984}.}
\footnotetext[5]{Reference~\cite{Murrell.Randic.Williams.Longuet-Higgins.ProcRSocLondA.1965}.}
\footnotetext[6]{Eq.~\eqref{}. Auxiliary basis sets for the EDF in $E^{\rm Rep}(S^{-1})$ 
from Eq.~\eqref{e:rep.murrell-etal.S1.oep}
are: `large' - aug-cc-pVDZ-jkfit for (H$_2$O)$_2$ and H$_2$O--HOCH$_3$ systems as well as
aug-cc-pVDZ-ri for (DMSO)$_2$ system;
`mini' - optimized small basis sets (see Supporting Information).}
%
\end{table*}
}
%
